diffusion, websites with 1 pc

### 2023-12-14 src/level_lisa_la.Rmd
local minor changes

# if distances are included, effect = year. 
# Rho is positive and sig, AR is positive and sig, BUT Wn(t-1) is negative and sig
```
## df for RF

# London = Islington 
help1 <- st_filter( la.sf, cities.sf) %>% as_tibble %>% dplyr::select(LAD21CD) %>% 
  left_join(df, by = c("LAD21CD"="ladcd")) %>% dplyr::select(LAD21CD, year, n)

help1 <- st_filter( la.sf, cities.sf) %>% as_tibble %>% dplyr::select(LAD21NM,LAD21CD) %>% 
  mutate(cities = c("Leicester",
                    "Bristol",
                    "Manchester",
                    "Liverpool",
                    "Sheffield",
                    "Birmingham",
                    "Leeds",
                    "London",
                    "Edinburgh",
                    "Glasgow"))

dist$dist.city.name <- names(dist)[apply(dist[,1:9], MARGIN = 1, FUN = which.min)]
help2 <- dist %>% left_join(help1, by = c("dist.city.name" = "cities")) %>% 
  rename(nearest.city.LAD21CD = LAD21CD) %>% 
  dplyr::select(ladcd, nearest.city.LAD21CD)

knn.l <- nb2listw(knn)

df <- df %>% drop_na() %>% group_by(year) %>% 
  mutate(n.slag = lag.listw(knn.l, n)) %>% 
  group_by(ladcd) %>% 
  mutate(n.l.slag = dplyr::lag(n.slag, n=1, order_by=year)) %>% 
  left_join(help2, by = c("ladcd" = "ladcd"))

df <- df %>% left_join(df %>% dplyr::select(ladcd,year, n) %>% 
                         rename(n.nearest.city = n), 
                       by = c("nearest.city.LAD21CD" = "ladcd",
                              "year" = "year")) %>% 
  dplyr::select(-c(LAD21NMW, OBJECTID, BNG_E, BNG_N, LONG, LAT, SHAPE_Length)) %>% 
  relocate(LAD21NM, .after = ladcd)

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup)%>% dplyr::select(LAD21CD, RGN21CD)

df <- df %>% left_join(lookup.region, by = c("ladcd" = "LAD21CD")) %>% 
  relocate(RGN21CD, .after=year)
```

## RF

### train

```{r}
library(caret)
library(randomForest)

# CV
tc <- trainControl(method = "cv",
                   number = 10,
                   savePredictions = 'final')

# London region: E12000007
# training dataset
tr.df <- df %>% ungroup() %>% filter(RGN21CD!="E12000007"|
                                     RGN21CD!="E12000008")

set.seed(71)
m <- train(n ~ density + area + dist + dist.retail + London +
             n.slag + year + n.nearest.city, #n.l.slag
           data = tr.df,
           trControl = tc,
           method = "rf", 
           importance = TRUE,
           na.action = na.omit)
summary(m)
plot(m)
m

varimp_mars <- varImp(m)
plot(varimp_mars, main="Variable Importance")
```

### test

```{r}
pred <- predict(m, df %>% ungroup() %>% filter(RGN21CD=="E12000008"), na.action = na.pass)
length(pred)

df %>% ungroup() %>% filter(RGN21CD=="E12000008") %>% filter(if_any(everything(), is.na))

pred <- cbind(pred %>% as_tibble(), df %>% ungroup() %>% filter(RGN21CD=="E12000008"))
postResample(pred = pred$value, obs = pred$n) ## 0.99
```
## Firms

```{r}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  dplyr::select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

## time slices

```{r}
hepl <- df %>% createTimeSlices(initialWindow = 5,
                        horizon = 1,
                        fixedWindow = F)

#Adding t-1 lag for n

set.seed(71)
m.test <- train(n ~ area + dist + dist.retail + London + #density
             n.slag + year + n.nearest.city + n.l.slag,
           data = df %>% filter(year < 1998),
           trControl = tc,
           method = "rf", 
           importance = TRUE,
           na.action = na.omit)
summary(m.test)
plot(m.test)
m.test

varimp_mars <- varImp(m.test)
plot(varimp_mars, main="Variable Importance")

pred <- predict(m.test, df %>% ungroup() %>% filter(year==1998), na.action = na.pass)
length(pred)

pred <- cbind(pred %>% as_tibble(), df %>% ungroup() %>% filter(year==1998))
postResample(pred = pred$value, obs = pred$n) ## 0.99
```

>>>>

# if distances are included, effect = year. 
# Rho is positive and sig, AR is positive and sig, BUT Wn(t-1) is negative and sig
```
